The resurgence of the linear optics \sihui{quantum} interferometer --- recent advances \& applications

### 2019-01-04 submitted_v2/review_v3/paper.tex
Reflected changes in reply-to-referee file.

%Without the use of repeaters, it has been shown that the rate transmission of a 
%channel with loss without entanglement assistance has a linear fallout 
%\cite{bib:TGW14}, and its bound is known as the Takeoka-Guha-Wilde (TGW) bound. 
%The minimal resources required to exceed the TGW bound is a subject of active 
%research, and so far it has been shown that the performance of the repeater 
%schemes of Ewert-Bergmann-van Loock \cite{bib:Ewert16}, and Sinclair et al. 
%\cite{bib:Sinclair14} are able to exceed the TGW bound. 
Without the use of repeaters it has been shown that the asymptotic rate of transmission of a channel with loss without entanglement assistance has a linear fallout according to the Takeoka-Guha-Wilde (TGW) bound \cite{bib:TGW14} and the tighter Pirandola-Laurenza-Ottaviani-Banchi (PLOB) bound \cite{PLOB17}. In particular, the PLOB bound coincides with the best known lower bound \cite{PGBL09} and establishes the two-way quantum capacity of the lossy channel. These results were refined by Wilde, Tomamichel and Berta who derived non-asymptotic rates that are applicable to protocols using such a channel finitely many times \cite{WTB17}. Others have generalized the TGW bound for arbitrary network topology \cite{AML16}. The minimal resources required to exceed the linear fallout is a subject of active research, and so far it has been beaten by the repeater schemes of Ewert-Bergmann-van Loock \cite{bib:Ewert16}, and Sinclair et al.~\cite{bib:Sinclair14}.

>>>>

%Without the use of repeaters, it has been shown that the rate transmission of a 
%channel with loss without entanglement assistance has a linear fallout 
%\cite{bib:TGW14}, and its bound is known as the Takeoka-Guha-Wilde (TGW) bound. 
%The minimal resources required to exceed the TGW bound is a subject of active 
%research, and so far it has been shown that the performance of the repeater 
%schemes of Ewert-Bergmann-van Loock \cite{bib:Ewert16}, and Sinclair et al. 
%\cite{bib:Sinclair14} are able to exceed the TGW bound. 
Without the use of repeaters it has been shown that the asymptotic rate of transmission of a channel with loss without entanglement assistance has a linear fallout according to the Takeoka-Guha-Wilde (TGW) bound \cite{bib:TGW14} and the tighter Pirandola-Laurenza-Ottaviani-Banchi (PLOB) bound \cite{PLOB17}. In particular, the PLOB bound coincides with the best known lower bound \cite{PGBL09} and establishes the two-way quantum capacity of the lossy channel. PLOB showed that if the transmission rate is above the PLOB bound, the error will not vanish asymptotically. These results were refined by Wilde, Tomamichel and Berta who showed that with a rate above the PLOB bound one will decode wrongly with certainty, and also derived non-asymptotic bounds that are applicable when the channel is used only a finite number of times \cite{WTB17}. Others have generalized the TGW bound for arbitrary network topology \cite{AML16}. The minimal resources required to exceed the linear fallout is a subject of active research, and so far it has been beaten by the repeater schemes of Ewert-Bergmann-van Loock \cite{bib:Ewert16}, and Sinclair et al.~\cite{bib:Sinclair14}.
